Astr 513: Final Project

### 2016-04-29 Final_Project/ms.tex
Created new correlation matrices and added them to the paper. Put in section labels for all sections. Added sections about Planck.
Started writing the Planck section.

\usepackage{todonotes}
\newcommand\TM[1]{\todo[color=green!40, inline, size=\small]{TM: #1}}
\newcommand\EW[1]{\todo[color=blue!40, inline, size=\small]{TM: #1}}
\newcommand\LC[1]{\todo[color=magenta!40, inline, size=\small]{TM: #1}}

@@

\section{Type Ia Supernovae}
\TM{TODO: Complete this section.}

@@

\begin{figure}
 \includegraphics[width=\linewidth]{figures/correlation.eps}
 \caption{Correlation matrix of $\mu_0(z)$ from the
 \citet{betoule2014} sample.}
 \label{fig:cmatrix}
\end{figure}

@@

\subsection{Results}
\TM{Discuss the results and show the corner plot. Example plot included.}

@@

%\section*{References}
%
%\begin{enumerate}
%  \item test
%\end{enumerate}

>>>>

\usepackage{todonotes}
\newcommand\TM[1]{\todo[color=green!40, inline, size=\small]{TM: #1}}
\newcommand\EW[1]{\todo[color=blue!40, inline, size=\small]{TM: #1}}
\newcommand\LC[1]{\todo[color=magenta!40, inline, size=\small]{TM: #1}}
\newcommand\Planck{{\it Planck}\ }

@@

\section{Type Ia Supernovae}
\label{sec:SNIa}
\TM{TODO: Complete this section.}

\section{Planck 2015 Results}
\label{sec:planck}
In 2009 the European Space Agency launched the \Planck satellite in order
to measure the Cosmis Microwave Background (CMB) with unparalleled precision.
By measuring the small anisotropies in the temperature of the CMB across
the entire sky one calculates the angular power spectrum, which can be
predicted from first principles (see, e.g., \citet{dodelson2003}).

@@

\begin{figure}
 \includegraphics[width=\linewidth]{figures/Betoule_correlation.eps}
 \caption{Correlation matrix of $\mu_0(z)$ from the
 \citet{betoule2014} sample.}
 \label{fig:cmatrix}
\end{figure}

\begin{figure}
 \includegraphics[width=\linewidth]{figures/Rest_correlation.eps}
 \caption{Correlation matrix of $\mu_0(z)$ from the
 \citet{rest2014} sample.}
 \label{fig:cmatrix}
\end{figure}

@@

\subsection{Planck Priors}
\label{sec:planck_priors}

\section{Results}
\label{sec:results}
\TM{Discuss the results and show the corner plots. Example plot included.
  We should have one corner plot without priors and one with priors.}

@@

\section{Conclusions}
\label{sec:conclusions}
\TM{Talk about how the inclusions if priors changes the analysis.
  State whether the priors are strong or uninformative.}
